Adopting agile in the large: motivations, success factors and challenges

### 2014-01-13 journal/article.tex
Note on multiple papers for a single case

>>>>

It was quite common that a single transformation case was described by many
papers. For example, one paper would highlight the viewpoint of developers [ref.
salesforce?], and another would consider the transformation from user experience
designers' point of view [ref. salesforce?]. In stead of using the most complete
paper as suggested by Kitchenham \cite{Kitchenham2007}, we combined the results
presented in each paper and considered the case as a single unit. By doing this
we avoided bias caused by duplicate publications, and were enabled to have a
more detailed view of the case organization.
